---
title: ""
subtitle: ""
description: "Single-cell RNA-seq"
author: 
  - name: "[Vincent Gélinas, M.Sc.](https://compbio.ca/team/)"
  - name: "[Charles Joly Beauparlant, Ph.D](https://compbio.ca/teams/charles-joly-beauparlant/)"
date: last-modified
date-format: "DD-MM-YYYY"
title-block-banner: "#1A468F"
title-block-banner-color: "white"
last-modified:
backgroundcolor: "white"
execute:
  echo: false
format:
  html:
    tabsets: true
    toc: true
    toc-depth: 3
    toc-title: Contents
    toc-location: left
    self-contained: true
    cards: true
    css: ".report/style.css"
    linkcolor: "#9DD3E4"
callout-icon: false
include-after-body:
  text: |
    &nbsp;
    <footer>
    <hr/>
    <p class="footer-information" style="text-align: center;">Produced by <a href="https://compbio.ca/">Arnaud Droit’s Computational Biology Laboratory</a></p>
     <p class="footer-information" style="text-align: center;"><span style="color: white;">Centre de recherche du CHU de Québec - Université Laval</span></p>
     <p class="footer-information" style="text-align: center;"><span style="color: white;">2705, boulevard Laurier, Québec (QC), G1V4G2, T-R5711</span></p>
    </p>
        &nbsp;

    </footer>
---

```{r libraries, echo = FALSE}
suppressMessages(library(ggplot2))
suppressMessages(library(patchwork))
suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(dplyr))
suppressMessages(library(ggiraph))
suppressMessages(library(ggrastr))
suppressMessages(library(gridExtra))
suppressMessages(library(ComplexHeatmap))
suppressMessages(library(grid))
suppressMessages(library(knitr))
suppressMessages(library(DT))
suppressMessages(library(gprofiler2))
```

## Introduction

The goal of this report is to portrait the statistical insights of the single-cell RNA-seq analysis to better diagnose the SingleCell::analyze_integrated function that was use on the given Seurat object. 

## Methods

Analyses were performed using [Seurat](https://satijalab.org/seurat/) v*4.4.0 package [1]. For Uniform Manifold Approximation and Projection (UMAPs) and clusters computing, 20 PCA dimensions were used, and a series of resolution from 0.1 to 2 were chosen for clustering. All graphical representation were done using [ggplot2](https://ggplot2.tidyverse.org/reference/scale_brewer.html) v3.5.1 from the [tidyverse](https://www.tidyverse.org/) v2.0.0 package tool [2]. All R analyses were done in R v4.3.1 [3].

[1] Hao, Yuhan et al. Integrated analysis of multimodal single-cell data. Cell, Volume 184, Issue 13, 3573 - 3587.e29

[2] Wickham, H. (2011). ggplot2. Wiley Interdisciplinary Reviews: Computational
Statistics, 3(2), 180-185

[3] R: Team, R. Core. "R: A language and environment for statistical computing."
(2013): 201.

### Softwares

::: {.callout-note collapse=true .session-info}

## R session infos

```{r}
sessionInfo()
```

:::

